Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-01 snapshot_system/failover.tex
updated graphs
updates

@@

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. FSBs used by VM},
                ymin=0,
                mark options=solid,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
		\addplot table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                \addplot+[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}
The snapshot availability of is a VM is the likelyhood that
there is no  data loss for all its file blocks.
With replication degree $r$, the likelyhood of
a file block block is the probability that  
all of its replicas appear in $d$ failed machines. 
Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.

@@

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
                cycle multi list={
                    mline\nextlist
                    [2 of]mmark*\nextlist
                },
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                \addlegendentry{$VC\,20$ (measured)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
                \addlegendentry{$VC\,2500$ (worst-case)}
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                \addlegendentry{$VO\,5$ (measured)}
                \addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                \addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for
  varying degrees of block sharing (i.e. average number of VMs that use a
  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
  Graph shown for 100 machine cluster.
  }
  \label{fig:vm-availability}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. VMs sharing FSB},
                cycle list name=mline,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig:fsb-links}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. FSBs used by VM},
                ymin=0,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}
The snapshot availability of is a VM is the likelyhood that
there is no  data loss for all its file blocks.
With replication degree $r$, the likelyhood of
a file block block is the probability that  
all of its replicas appear in $d$ failed machines. 
Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.

@@

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
                cycle multi list={
                    mline\nextlist
                    [2 of]mmark*\nextlist
                },
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                \addlegendentry{$VC\,1250$ (estimated)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
                \addlegendentry{$VC\,2500$ (worst-case)}
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                \addlegendentry{$VO\,6.3$ (optimistic)}
                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                %\addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for
  varying degrees of block sharing (i.e. average number of VMs that use a
  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
  Graph shown for 100 machine cluster.
  }
  \label{fig:vm-availability}
\end{figure}
